Sketch Recognition and Understanding

### 2009-08-17 draft/chapterSurvey.tex

\chapter{Literature Survey}
\label{sec:survey}
% this will contians only the finished work .... and my comments to view the old survey see the file
%draft_chaptersurvey 
%\section{Introduction }
%\label{sec:Introduction}
The history of pen and sketch based computing goes back to 1963 with Ivan Sutherland's SKETCHPAD \cite{sutherlandsketch}, which used a light pen to draw on the monitor to create circuit diagrams. Current technology and the increase in computing power have increased the abilities of such interfaces and allowed the implementation of fully sketching systems. Over the years, many other sketching based systems have been developed. Through this history most system focused on building the interactive interfaces to assist users while entering information to the computer. To demonstrate our system inspiration we will first present current research in the area of sketch recognition. In Section \ref{sec:preprocessing}, preprocessing and segmentation methods will be discussed in details. Later, symbol recognition methods will be presented and analyzed in Section \ref{sec:symbolrecogntion}.

% i need to write a history then small introduction to the survey...
%  i have to state that the next  sections will generally group segmentation and symbol recognition task. 
\section{Preprocessing and Segmentation}
\label{sec:preprocessing}
  In a system that supports free hand sketching, sketching should be as natural as possible. This means that the user can draw symbols using single or multiple strokes without constrains. The goal of a sketch system is making the user feel that using the system is nearly the same as using a pencil and paper. But sketches are incomplete drawings that are sloppy and messy, for example figures \ref{fig:Overshootandundershoot} and \ref{fig:overstroked} show examples of messy sketches drawn by users. This led researchers to perform sort of preprocessing before starting the sketch recognition task itself. The next sections explain different preprocessing techniques.

@@

 Systems that employ such representation must first pre-process strokes to break them into geometric primitives ( section \ref{sec:preprocessing} reviews on preprocessing methods). Recognition can then be treated as sub graph matching problem or constrain satisfaction problem.

@@

%\subsection{The Algorithm}
%%\label{sec:ParticleSwarmAlgorithm} 
%\begin{verbatim}
% Initialize 
%    Generate N particles with M dimensions (P_i...P_N) 
%    Generate velocities for each particle for M dimension randomly. 
% Repeat till Maximum number of iteration OR Fitness 
%         For each particle P_i do the following 
%                Compute fitness  
%                Determine Lbest  
%                Check if need to change Gbest. 
%                Compute the Velocity for each dimension using eq. 
%                Check if maximum Velocity reach and limit it 
%                update particle values 
%          end . 
%        Improve all particle positions 
%  end 
%  
%  Final solution reaches in Gbest.       
%        
%        
%\end{verbatim}

>>>>

\chapter{Literature Survey}
\label{sec:survey}
% this will contians only the finished work .... and my comments to view the old survey see the file
%draft_chaptersurvey 
%\section{Introduction }
%\label{sec:Introduction}
The history of pen and sketch based computing goes back to 1963 with Ivan Sutherland's SKETCHPAD \cite{sutherlandsketch}, which used a light pen to draw on the monitor to create circuit diagrams. Current technology and the increase in computing power have increased the abilities of such interfaces and allowed the implementation of fully sketching systems. Over the years, many other sketching based systems have been developed. Through this history most system focused on building the interactive interfaces to assist users while entering information to the computer. To demonstrate our system inspiration we will first present current research in the area of sketch recognition. In Section \ref{sec:preprocessingSeg}, preprocessing and segmentation methods will be discussed in details. Later, symbol recognition methods will be presented and analyzed in Section \ref{sec:symbolrecogntion}.

% i need to write a history then small introduction to the survey...
%  i have to state that the next  sections will generally group segmentation and symbol recognition task. 
\section{Preprocessing and Segmentation}
\label{sec:preprocessingSeg}
  In a system that supports free hand sketching, sketching should be as natural as possible. This means that the user can draw symbols using single or multiple strokes without constrains. The goal of a sketch system is making the user feel that using the system is nearly the same as using a pencil and paper. But sketches are incomplete drawings that are sloppy and messy, for example figures \ref{fig:Overshootandundershoot} and \ref{fig:overstroked} show examples of messy sketches drawn by users. This led researchers to perform sort of preprocessing before starting the sketch recognition task itself. The next sections explain different preprocessing techniques.

@@

 Systems that employ such representation must first pre-process strokes to break them into geometric primitives ( section \ref{sec:preprocessingSeg} reviews on preprocessing methods). Recognition can then be treated as sub graph matching problem or constrain satisfaction problem.

@@

\subsection{The Algorithm}
\label{sec:ParticleSwarmAlgorithm}

This section will discribe each step of the PSO Algorithm. Intially, the swarm partilces are created and each of which is a binary vector crossponding to candidate solution. Additionally, the velocities of each particle is initialized at random by drawing uniformly real values from the range [0.0 to 1.0]. Then the evolutionary process of particle movement is iterated until maximum number of eteration or a fittness error achieved. At each iteration,  the fitness value of each partilce is evaluated, and the particles individual local best and global best is updated. The particle position is adjusted as follow; the velocities is computed using Equation \ref{eq:Swarm}. Equation \ref{eq:vmax} is used to scale the velocity to values between 0 and 1 which will serve asa probability that the corresponding bit takes the value of 1. The particles bit vectors are updated by Equation \ref{eq:descrite} according to their velocity which measure the trajectory to the target solution based on local experience ($lbest_{i}$) and global intelligence ($gbest_{i}$). Before the end of the iteratin the particle may move to a refined location based on the refine procedure used.

\begin{verbatim}
Initialize 
  1. Generate N particles with M dimensions (P_i...P_N) 
  2. Generate velocities for each particle for M dimension randomly. 
  3. Repeat till Maximum number of iteration OR ErrorThreshold  
         For each particle P_i do the following 
         3.a   Compute fitness  (fitness)
         3.b   Determine Lbest  
               if (lbest_fitness<fitness)
                  3.b.1   lbest=P_i
         3.c      Determine Gbest.
               if (lGest_fitness<fitness)
                  3.c.1   lGest=P_i
         3.d   Compute the Velocity for each dimension using eq.3.2 
         3.e   Bound Velocity using eq.3.4
         3.f   Update particle values using eq. 3.3
         3.g   Refine the location of the particle
         end .
     end 
4. return Gbest
\end{verbatim}
